Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Weight and Convex Input Constraints

### 2025-05-02 manuscript.tex
Refactor code structure for improved readability and maintainability

To validate the effectiveness of the proposed CONAC, a real-time experiment was conducted on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
The OpenCR1.0 board \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
\color{red}
The experimental setup consisted of a two-link manipulator with a 2-DOF arm, equipped with two @@@@@ servos. 
The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the servos via controller area network (CAN) communication.
\color{black}
The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, the estimated system parameters are provided in Table~\ref{table:system:params}.

@@

% ------------------------------------
% Robot Model Parameters
% -----------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
    \centering
    \begin{tabular}{c m{9.5em} c c c }
    % \begin{tabular}{c c c c c}
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass & \multicolumn{2}{c}{2.465 (kg)} \\
    \hline
    $l_p$  & Length & 0.2 (m) & 0.18 (m) \\
    \hline
    ${l_c}_p$ & Center of mass & 0.139 (m) & 0.087 (m) \\
    \hline
    $b_p$   & Viscous friction coef. & \multicolumn{2}{c}{0.1 (Nms)} \\
    \hline
    ${f_c}_p$  & Coulomb friction coef. & \multicolumn{2}{c}{0.24 (Nm)} \\
    \hline
    ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
    \hline
    $I_p$  & Inertia & 0.069 (kgm\textsuperscript{2}) & 0.015 (kgm\textsuperscript{2}) \\
    \hline
    \end{tabular}
    \label{table:system:params}
\end{table}

@@

% ------------------------------------
% Reference Trajectory
% ------------------------------------
The desired trajectory for $\q=\left(q_1,q_2\right)^\top $ was generated using fifth-order polynomial functions $\mypoly^5(\mv{x}_1,\mv{x}_2,t_f,t)$, to satisfy the initial $\mv{x}_1$ and final $\mv{x}_2$ angle conditions and zero velocities of the joints, where $t_f$ is the time duration.
The desired trajectory is defined as follows:
\begin{equation}
    \qd(t) 
    \!=\! 
    \begin{pmatrix}
        {q_d}_1\\{q_d}_2
    \end{pmatrix}
    \!=\!
    \begin{cases}
    \mypoly^5({\qd}_0,{\qd}_1,t_f,t),
        \!&\!
        \text{if } 0\!\le\!t\!<\!t_f 
        ,
        \\
    \mypoly^5({\qd}_1,{\qd}_2,t_f,t-t_f),
        \!&\!
        \text{if } t_f\!\le\!t\!<\!2t_f 
        ,
        \\
    \mypoly^5({\qd}_2,{\qd}_1,t_f,t-2t_f),
        \!&\! 
        \text{if } 2t_f\!\le\!t\!<\!3t_f 
        .
        \\
    \mypoly^5({\qd}_1,{\qd}_0,t_f,t-3t_f),
        \!&\!    
        \text{if } 3t_f\!\le\!t\!<\!4t_f 
        ,
        \\
    \end{cases}
    \label{eq:desired trajectory}
\end{equation}
where ${\qd}_0:=\left(-\tfrac{1}{2}\pi,0\right)^\top$, ${\qd}_1:=\left(\tfrac{1}{4}\pi,-\tfrac{1}{2}\pi\right)^\top$, ${\qd}_2:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top$, and $t_f=3$ s.
To demonstrate the learning capability of NN, the desired trajectory was applied twice; let us call the first and second iterations of the reference trajectory as Episode $1$ and Episode $2$, respectively.

@@

% ------------------------------------
% Control Input Saturation
% ------------------------------------
To demonstrate the effectiveness of the proposed CONAC to handle the combination of the convex input constraints, the saturation function is defined to project the control input onto following convex domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:robot:sat}, where
%
\begin{subequations}
    \begin{align}
        \Theta_{\mysat, {\rbu}}
        :=&
        \left\{
            \rbu
            \mid
            \norm{\rbu} \le 
            10
            % \overline\tau
        \right\}
        \label{eq:sat:norm}
        ,
        \\
        \Theta_{\mysat, {\tau_2}}
        :=&
        \left\{
            \tau_2
            \mid
            \vert{\tau_2}\vert \le 
            2.5
            % \overline\tau_2
        \right\}
        .
        \label{eq:sat:tau2}
    \end{align}
    \label{eq:sat}
\end{subequations}
%
These domains \eqref{eq:sat:norm} and \eqref{eq:sat:tau2} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the second link actuator, respectively.

@@

To handle the input saturation, the proposed CONAC was implemented with the input bound constraint for second link $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ \eqref{eq:cstr:input:bound} and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
\begin{equation}
    c_{\overline\tau_2}     
    =
    \tau_2-\overline\tau_2
    \le 0
    ,
    \;
    c_{\underline\tau_2} 
    =
    \underline\tau_2-\tau_2
    \le 0
    ,
    \;
    c_{\rbu}
    =
    \tfrac{1}{2}
    (
        \norm{\rbu}-\overline\tau
    )^2 
    <0
    ,
    \label{eq:sim:cstr:CONAC}
\end{equation}
where $\overline\tau_2=-\underline{\tau}_2=2.5$ are the absolute bound of the second link actuator, and $\overline\tau=10$ is the maximum feasible norm of the control input.
Hence, (C$_1$) is possible to use full capability of the actuator.
The weight constraints $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ were also considered in the CONAC.
As described in \eqref{eq:control:est}, the control input is equal to the output of the NN, and the adaptation law is defined in \eqref{eq:adaptation law}.

The update rate of the Lagrange multipliers was set to $\beta_{\theta_i}=10^{-3},\ \forall i\in[0,\cdots,k]$, and $\beta_{\rbu}=10$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{3}$.

@@

On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed (C$_1$).
The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu,\ \mv{\zeta}\vert_{t=0} = \mv{0}_{2\times1}$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$, and $\mm{B}_\zeta\in\R^{n\times n}$.
The auxiliary state $\mv{\zeta}$ is affected by the saturated control input $\Delta\rbu$, whose entry is defined as $\Delta\tau_{i} = 
\tau_{i}-\max(\underline\tau_i,\min(\overline\tau_i,\tau_i)),\ \forall i\in\{1,2\}$.
Since, the auxiliary system only considers the input bound constraint, $\overline{\tau}_1$ is set to $9.682$ to approximately match the maximum allowable norm of the control input $\overline\tau$, (\ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$, and $\overline{\tau}_2=2.5$ and $\overline{\tau}=10$).

@@

The matrices of the auxiliary system are set to $\mm{A}_\zeta=\mydiag([-10,-10])$ and $\mm{B}_\zeta=\mydiag([10^3,10^3])$, considering the tradeoff between the sensitivity of the control saturation, and the convergence speed.
\MSRY{sensitivity와 convergence에 대해서 더 설명이 필요한가?}

@@

To investigate the effect of the update rate of Lagrange multipliers, (C$_3$) was implemented with small $\beta_i$ values, which are set to $\beta_{\rbu}=1$, and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{2}$.
The remaining parameters are the same as (C$_1$).

@@

% ------------------------------------
% Controller Parameters
% ------------------------------------
For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix. 
The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.1,0.1]$, and the same random seed.
Each NN architecture had two hidden layers with four nodes (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$), and the adaptation gain was set to $\alpha=0.5$.
The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
The sampling rate of the controller was $250$ Hz considering the real-time implementation, and $1000$ Hz for the simulation.
\MSRY{CAN Hz?}
To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$), avoiding the violation of the weight constraints.

@@

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in simulation}
    \label{table:controller}
    \centering
    \begin{tabular}{c l l}
    \hline
        \!&\!\bf{Description}\!&\!\bf{Input Constraint}\!\\
    \hline
    \hline
        (C$_1$)\!&\!large $\beta_j$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau}_2=2.5$ \\
    \hline
        (C$_2$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!9.682,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!2.5$\!\\
    \hline
        (C$_3$)\!&\!small $\beta_j$\!&\!$\overline{\tau}=10,\overline{\tau}_2=-\underline{\tau_2}=2.5$ \\
    \hline
        (C$_4$)\!&\!no $\rbu$ constraints\!&\!$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
    \hline
    \end{tabular}
    \label{table:controllers}
\end{table}

>>>>

To validate the effectiveness of the proposed CONAC, a real-time experiment was conducted on a two-link manipulator, as shown in Fig.~\ref{fig:ctrl:exp:set}. 
The OpenCR1.0 board \cite{opencr} with a 32-bit ARM Cortex and a 216 MHz clock frequency was used for the real-time implementation.
\DHHO{
The experimental setup consisted of a two-link manipulator actuated by two Cubemars AK10-90 servo motors. 
The servos were controlled using the OpenCR1.0 board which transmits the reference angle to the servos via controller area network (CAN) communication.
}
The system dynamics of the two-link manipulator is described in \eqref{eq:sys1}, the estimated system parameters are provided in Table~\ref{table:system:params}.

@@

% ------------------------------------
% Robot Model Parameters
% -----------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Two-link manipulator parameters of $p\textsuperscript{th}$ link.}
    \centering
    \begin{tabular}{c m{9.5em} c c c }
    % \begin{tabular}{c c c c c}
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass & \multicolumn{2}{c}{2.465 (kg)} \\
    \hline
    $l_p$  & Length & \multicolumn{2}{c}{0.2 (m)} \\  
    \hline
    ${l_c}_p$ & Center of mass & \multicolumn{2}{c}{0.139 (m)} \\
    \hline
    $b_p$   & Viscous friction coef. & \multicolumn{2}{c}{0.1 (Nms)} \\
    \hline
    ${f_c}_p$  & Coulomb friction coef. & \multicolumn{2}{c}{0.24 (Nm)} \\
    \hline
    ${f_s}_p$  & Static friction coef. &  0.3 (Nm) & 0.2 (Nm) \\
    \hline
    $I_p$  & Inertia & \multicolumn{2}{c} {0.069 (kgm\textsuperscript{2})} \\
    \hline
    \end{tabular}
    \label{table:system:params}
\end{table}

@@

% ------------------------------------
% Reference Trajectory
% ------------------------------------
The desired trajectory for $\q=\left(q_1,q_2\right)^\top $ was generated using fifth-order polynomial functions $\mypoly^5(\mv{x}_1,\mv{x}_2,t_f,t)$, to satisfy the initial $\mv{x}_1$ and final $\mv{x}_2$ angle conditions and zero velocities of the joints, where $t_f$ is the time duration.
The desired trajectory is defined as follows:
\begin{equation}
    \qd(t) 
    \!=\! 
    \begin{pmatrix}
        {q_d}_1\\{q_d}_2
    \end{pmatrix}
    \!=\!
    \begin{cases}
    \mypoly^5({\qd}_0,{\qd}_1,t_f,t),
        \!&\!
        \text{if } 0\!\le\!t\!<\!t_f 
        ,
        \\
    \mypoly^5({\qd}_1,{\qd}_2,t_f,t-t_f),
        \!&\!
        \text{if } t_f\!\le\!t\!<\!2t_f 
        ,
        \\
    \mypoly^5({\qd}_2,{\qd}_1,t_f,t-2t_f),
        \!&\! 
        \text{if } 2t_f\!\le\!t\!<\!3t_f 
        .
        \\
    \mypoly^5({\qd}_1,{\qd}_0,t_f,t-3t_f),
        \!&\!    
        \text{if } 3t_f\!\le\!t\!<\!4t_f 
        ,
        \\
    \end{cases}
    \label{eq:desired trajectory}
\end{equation}
where ${\qd}_0:=\left(-\tfrac{1}{3}\pi,\tfrac{1}{3}\pi\right)^\top$, ${\qd}_1:=\left(\tfrac{1}{4}\pi,-\tfrac{1}{2}\pi\right)^\top$, ${\qd}_2:=\left(-\tfrac{1}{4}\pi,\tfrac{1}{4}\pi\right)^\top$, and $t_f=3$ s.
To demonstrate the learning capability of NN, the desired trajectory was applied twice; let us call the first and second iterations of the reference trajectory as Episode $1$ and Episode $2$, respectively.

@@

% ------------------------------------
% Control Input Saturation
% ------------------------------------
To demonstrate the effectiveness of the proposed CONAC to handle the combination of the convex input constraints, the saturation function is defined to project the control input onto following convex domain $\Theta_{\mysat}:=\left\{\Theta_{\mysat, {\rbu}}\cap\Theta_{\mysat, {\tau_2}}\right\}$ as depicted in Fig.~\ref{fig:robot:sat}, where
%
\begin{subequations}
    \begin{align}
        \Theta_{\mysat, {\rbu}}
        :=&
        \left\{
            \rbu
            \mid
            \norm{\rbu} \le 
            11
            % \overline\tau
        \right\}
        \label{eq:sat:norm}
        ,
        \\
        \Theta_{\mysat, {\tau_2}}
        :=&
        \left\{
            \tau_2
            \mid
            \vert{\tau_2}\vert \le 
            3.5
            % \overline\tau_2
        \right\}
        .
        \label{eq:sat:tau2}
    \end{align}
    \label{eq:sat}
\end{subequations}
%
These domains \eqref{eq:sat:norm} and \eqref{eq:sat:tau2} can be physically interpreted as a combination of the voltage source limitation of the actuators and the torque limitation of the second link actuator, respectively.

@@

To handle the input saturation, the proposed CONAC was implemented with the input bound constraint for second link $c_{\overline\tau_2}$ and $c_{\underline\tau_2}$ \eqref{eq:cstr:input:bound} and the nonlinear input norm constraint $c_{\rbu}$ \eqref{eq:cstr:input:norm}, as follows:
\begin{equation}
    c_{\overline\tau_2}     
    =
    \tau_2-\overline\tau_2
    \le 0
    ,
    \;
    c_{\underline\tau_2} 
    =
    \underline\tau_2-\tau_2
    \le 0
    ,
    \;
    c_{\rbu}
    =
    \tfrac{1}{2}
    (
        \norm{\rbu}-\overline\tau
    )^2 
    <0
    ,
    \label{eq:sim:cstr:CONAC}
\end{equation}
where $\overline\tau_2=-\underline{\tau}_2=3.5$ are the absolute bound of the second link actuator, and $\overline\tau=11$ is the maximum feasible norm of the control input.
Hence, (C$_1$) is possible to use full capability of the actuator.
The weight constraints $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ were also considered in the CONAC.
As described in \eqref{eq:control:est}, the control input is equal to the output of the NN, and the adaptation law is defined in \eqref{eq:adaptation law}.

The update rate of the Lagrange multipliers was set to $\beta_{\theta_i}=10^{0},\ \forall i\in[0,\cdots,k]$, and $\beta_{\rbu}=10^{1}$ and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{2}$.

@@

On the other hand, the existing auxiliary system \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} was used to compare with the proposed (C$_1$).
The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\rbu,\ \mv{\zeta}\vert_{t=0} = \mv{0}_{2\times1}$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta\in\R_{<0}^{n\times n}$, and $\mm{B}_\zeta\in\R^{n\times n}$.
The auxiliary state $\mv{\zeta}$ is affected by the saturated control input $\Delta\rbu$, whose entry is defined as $\Delta\tau_{i} = 
\tau_{i}-\max(\underline\tau_i,\min(\overline\tau_i,\tau_i)),\ \forall i\in\{1,2\}$.
Since, the auxiliary system only considers the input bound constraint, $\overline{\tau}_1$ is set to $10.428$ to approximately match the maximum allowable norm of the control input $\overline\tau$, (\ie $\overline{\tau}_1^2+\overline{\tau}_2^2=\overline{\tau}^2$, and $\overline{\tau}_2=3.5$ and $\overline{\tau}=11$).

@@

The matrices of the auxiliary system are set to $\mm{A}_\zeta=\mydiag([-10,-10])$ and $\mm{B}_\zeta=\mydiag([800,800])$, considering the tradeoff between the sensitivity of the control saturation, and the convergence speed.
\MSRY{sensitivity와 convergence에 대해서 더 설명이 필요한가?}

@@

To investigate the effect of the update rate of Lagrange multipliers, (C$_3$) was implemented with small $\beta_i$ values, which are set to $\beta_{\rbu}=10^{-1}$, and $\beta_{\overline{\tau}_2}=\beta_{\underline{\tau}_2}=10^{0}$.
The remaining parameters are the same as (C$_1$).

@@

% ------------------------------------
% Controller Parameters
% ------------------------------------
For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix. 
The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.5,0.5]$, and the same random seed.
Each NN architecture had two hidden layers with four nodes \DHHO{k=2? (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$)}, and the adaptation gain was set to $\alpha=0.2$.
The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
\DHHO{ simulation?
    The sampling rate of the controller was $250$ Hz considering the real-time implementation, and $1000$ Hz for the simulation.}
\MSRY{CAN Hz?}
To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$), avoiding the violation of the weight constraints.

@@

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in simulation}
    \label{table:controller}
    \centering
    \begin{tabular}{c l l}
    \hline
        \!&\!\bf{Description}\!&\!\bf{Input Constraint}\!\\
    \hline
    \hline
        (C$_1$)\!&\!large $\beta_j$\!&\!$\overline{\tau}=11,\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
    \hline
        (C$_2$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!10.428,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!3.5$\!\\
    \hline
        (C$_3$)\!&\!small $\beta_j$\!&\!$\overline{\tau}=11,\overline{\tau}_2=-\underline{\tau_2}=3.5$ \\
    \hline
        (C$_4$)\!&\!no $\rbu$ constraints\!&\!$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
    \hline
    \end{tabular}
    \label{table:controllers}
\end{table}
